Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-25 paper.tex
Revert "Acknowledge Massin's suggested optimisation"
This reverts commit ca7e2c414adda5ed7d700b66f18f9f46f147dc91.

Turns out this was actually Xavier's idea. ^^
Minor edit

\para{Lazy Insertion.}
Adding a hypothesis to a rule state is cheap, but not free: it involves one unification for each slot that the hypothesis may match, according to a discrimination tree index, followed by several operations on the variable indices.
We therefore delay insertions in two ways.
First, we observe that complete matches can only be generated once all slots have been filled.
Therefore, hypotheses are matched against slots and inserted into the variable indices only once we have found, for each slot, a hypothesis that may match the slot.
Second, we observe that the variable indices are only queried for hypotheses in a slot $i > 1$ when a match is added to slot $i - 1$.
Hence we delay the insertion of hypotheses at slot $i > 1$ until there is at least one match in slot $i - 1$.%
\footnote{This latter optimisation was suggested by Massin Guerdi.}

>>>>

\para{Lazy Insertion.}
Adding a hypothesis to a rule state is cheap, but not free: it involves one unification for each slot that the hypothesis may match, according to a discrimination tree index, followed by several operations on the variable indices.
We therefore delay insertions in two ways.
First, we observe that complete matches can only be generated once all slots have been filled.
Therefore, hypotheses are matched against slots and inserted into the variable indices only once we have found, for each slot, a hypothesis that may match the slot.
Second, we observe that the variable indices are only queried for hypotheses at a slot $i > 1$ when a match is added at slot $i - 1$.
Hence we delay the insertion of hypotheses at $i$ until there is at least one match in slot $i - 1$.
